\documentclass{article}
\usepackage[utf8]{inputenc}

% Package Imports
\usepackage{helvet} % Helvetica font
\usepackage[hmargin=1.25cm, vmargin=3cm]{geometry}
\usepackage[dvipsnames]{xcolor}
\usepackage[hidelinks]{hyperref} % hyper-links
\usepackage{eurosym} % € sign
\usepackage{parskip} % to set paragraph spacing
\usepackage{comment}

% Set Ups
\hypersetup{ % hyperref setup
    colorlinks = true,
    urlcolor = OliveGreen,
}


% Commands
\setlength{\parskip}{\medskipamount}
\makeatletter
    \newcommand{\@minipagerestore}{\setlength{\parskip}{0.3em}}
\makeatother

% \renewcommand{\familydefault}{\sfdefault}

\title{CV}
\author{Hendrik Mahlkow}
\date{July 2025}

\begin{document}

{\fontfamily{phv}\selectfont 
	    \LARGE{Dr. Hendrik Mahlkow}
	    %\headername{Hendrik Mahlkow}
	}\\
\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ADDRESS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.66\textwidth}
    Austrian Institute of Economic Research \\
    Arsenal, Objekt 20 \\
    1030 Vienna, Austria \\
    \newline
    Kiel Institute for the World Economy \\
    Kiellinie 66 \\
    24105 Kiel, Germany
\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth} 
    Tel: +49 431 8814-499 \\
    E-Mail: \href{mailto:mail@hendrikmahlkow.com}{mail@hendrikmahlkow.com} \\
    Web: \href{http://hendrikmahlkow.com}{hendrikmahlkow.com} 
\end{minipage}
\bigskip
\bigskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CURRENT POSITION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{comment}
\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont ACADEMIC POSITION} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth} 
    Researcher, Kiel Institute for the World Economy, since July 2019
\end{minipage}
\medskip
\end{comment}

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont CURRENT POSITIONS} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth} 
    Postdoctoral Research Fellow, Kiel Institute for the World Economy,  since 2024 \par
    Economist, Austrian Institute of Economic Research,  since 2023 \par
    Independent Consultant, since 2020 \par
    \begin{itemize}
        \item[-] Providing analytical support, economic modeling, data analysis, and programming
        \item[-] Various public sector stakeholders (e.g., UNIDO, German State Ministries) and private clients (e.g., GIZ GmbH, 21Staatskunst gGmbH)
    \end{itemize}
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PREVIOUS POSITION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont PREVIOUS POSITION} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth} 
    Junior Economist, Kiel Institute for the World Economy, 2019--2023 \par
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont EDUCATION} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    Ph.D. in Quantitative Economics, Kiel University, 2019--2024 \par
    Visiting Ph.D. Student, University of California, Berkeley, 2022--2023 \par
        \begin{itemize}
        \item[-] \textit{Department of Agriculture \& Resource Economics}, Host: Joe Shapiro
    \end{itemize}
    Advanced Studies Program in International Economic Policy Research, Kiel Institute:
    \begin{itemize}
        \item[-] \textit{Trade Policy Analysis with Gravity Models} by Yoto Yotov, December 2020 
        \item[-] \textit{Topics in International Trade} by Arnaud Costinot, December 2019
    \end{itemize}
    M.Sc. in Agricultural Economics, Humboldt University of Berlin, 2018 \par
    B.Sc. in Agricultural Sciences, Humboldt University of Berlin, 2012 \par
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUPLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont PUBLICATIONS} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    \href{https://www.doi.org/10.1088/1748-9326/ad34e9}{``Macroeconomic structural change likely increases inequality in India more than climate policy''} with Marian Leimbach, Michael Hübler, Gabriel Felbermayr, Mathias Kalkuhl, Jan Steckel, et al. \textit{Environmental Research Letters}, 2024. \par
    \href{http://doi.org/10.1111/1467-8268.12745}{``Long-run impacts of the conflict in Ukraine on food security in Africa''} with Lacina Balma, Tobias Heidland, Sebastian Jävervall, Adamon N. Mukasa \& Andinet Woldemichael. \textit{African Development Review}, 2024. \par
    \href{https://doi.org/10.1007/s10663-022-09561-w}{``Cutting through the value chain: The long-run effects of decoupling the East from the West''} with Gabriel Felbermayr \& Alexander Sandkamp, \textit{Empirica}, 2023. \par
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     WORKING PAPERS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont WORKING PAPER} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    \href{https://trade.ifw-kiel.de/KTTM/KITE_whitepaper.pdf}{``The KITE Model Suite: A Quantitative Framework for
International Trade Analysis''} with Julian Hinz and Joschka Wanner, 2025. \par
    \href{https://www.cesifo.org/en/publications/2023/working-paper/carbon-footprint-global-trade-imbalances}{``The Carbon Footprint of Global Trade Imbalances''} with Joschka Wanner, 2023. \par
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     WORK IN PROGRESS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont SELECTED WORK-IN-PROGRESS} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    ``How can trade policy mitigate climate change welfare impacts?'' single-authored.\par
    ``You can always go downtown? Weather effects and consumer responses'' with Annika Stechemesser.\par
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECT FUNDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{comment}
\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont PROJECT FUNDS} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    Carbon Border Tax Adjustment of the European Union, Bertelsmann Foundation (30,000 \euro{}), together with Gabriel Felbermayr, Sonja Peterson and Joschka Wanner, 2021. \par
    Economic Impact of COVID-19 on the Global South, German Federal Foreign Office (25,000 \euro{}), together with Katrin Kamin, Julian Hinz and Vincent Stamer, 2020. \par
    Global Value Chains after COVID-19, Impuls Foundation (10,000 \euro{}), together with Gabriel Felbermayr and Alexander Sandkamp, 2020. \par
    Greening the CAP by Harnessing the Power of Environmental Economics, foodwatch e. V. (15,000 \euro{}), together with  Gabriel Felbermayr, Ruth Delzeit and Anna-Katharina Jacobs, 2019.
\end{minipage}
\medskip
\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COMMENTARY & POLICY REPORTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont COMMENTARY \& POLICY REPORTS} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
  \href{https://www.unido.org/sites/default/files/unido-publications/2025-10/IID%20Policy%20Brief%2026%20-%20Resilient%20global%20supply%20chains%20in%20times%20of%20escalating%20trade%20costs.pdf}{``Resilient Global Supply Chains in Times of Escalating Trade Costs''} with Finn Ole Semrau, Frauke Steglich, Stefan Pahl, and Virpi Stucki, \textit{Insights on Industrial Development Policy Brief}, Issue 26, September 2025 \par
  \href{https://www.ifo.de/DocDL/sd-2025-06-zdg-kamin-mahlkow-welthandel-am-abgrund.pdf}{``Optimalzölle als EU-Strategie? Wie die EU (nicht) auf die US-Zölle reagieren sollte.''} with Katrin Kamin, \textit{ifo Schnelldienst}, June 2025.\par
  \href{https://www.wifo.ac.at/publication/pid/57956826}{``Free Trade, Anyone?
Different Trade Policy Scenarios Between Switzerland and the USA''} with Elisabeth Christen, Gabriel Felbermayr, 
Joschka Wanner, Martin Mosler, and Christoph A. Schaltegger, \textit{WIFO Study}, April 2025.\par
  \href{https://www.wirtschaftsdienst.eu/inhalt/jahr/2025/heft/4/beitrag/trumps-zoelle-chaotische-entkopplung.html}{``Trumps Zölle: chaotische Entkopplung''} with Sonali Chowdhry and Julian Hinz, \textit{Wirtschaftsdienst} (Leitartikel), April 2025.\par
    \href{https://eu.boell.org/sites/default/files/2025-03/2025_hbs_eu_policy_brief_trade_final.pdf}{``Trading partners? Europe's options against Trump's tariffs''} with Sonali Chowdhry and Julian Hinz, \textit{Böll EU Brief}, March 2025.\par
    \href{https://www.ifw-kiel.de/publications/time-to-be-open-sustainable-and-assertive-tariffs-on-chinese-bevs-and-retaliatory-measures-33083/}{``Time to be Open, Sustainable, and Assertive: Tariffs on Chinese BEVs and Retaliatory Measures''} with Gabriel Felbermayr, Klaus Friesenbichler, and Julian Hinz, \textit{Kiel Policy Brief}, July 2024.\par
    \href{https://www.fiw.ac.at/publications/trade-and-welfare-effects-of-new-trade-policy-instruments/}{``Trade and Welfare Effects of New Trade Policy Instruments''} with Yvonne Wolfmayr, Elisabeth Christen, Birgit Meyer, and Michael Pfaffermayr, Study for the Austrian Federal Ministry of Economics, January 2024.\par
    \href{https://www.europarl.europa.eu/RegData/etudes/IDAN/2023/754440/EXPO_IDA(2023)754440_EN.pdf}{``An analysis of the implementation of the EU-Canada Comprehensive Economic and Trade Agreement (CETA)''} with Julian Hinz, Carsten Brockhaus, Sonali Chowdhry, and Vasundhara Thakur, Study for the European Parliament, November 2023. \par
    \href{https://www.fiw.ac.at/2023/10/02/volkswirtschaftliche-kosten-der-russland-sanktionen/}{``Volkswirtschaftliche Kosten der Russland-Sanktionen''}, \textit{FIW Spotlight}, October 2023. \par
    \href{https://www.oekonomenstimme.org/artikel/2022/07/die-langfristigen-auswirkungen-einer-wirtschaftlichen-entkopplung-von-ost-und-west/}{``Die langfristigen Auswirkungen einer wirtschaftlichen Entkopplung von Ost und West''} with Alexander Sandkamp and Gabriel Felbermayr, \textit{Ökonomenstimme}, July 2022. \par
    \href{https://www.cesifo.org/en/publikationen/2022/working-paper/cutting-through-value-chain-long-run-effects-decoupling-east-west}{``Cutting through the Value Chain: The Long-Run Effects of Decoupling the East from the West''} with Gabriel Felbermayr and Alexander Sandkamp, \textit{EconPol Policy Brief}, ifo Institute, April 2022. \par
    \href{https://www.megatrends-afrika.de/publikation/mit-der-russischen-invasion-der-ukraine-droht-langfristige-ernaehrungsunsicherheit-in-afrika}{``Mit der russischen Invasion der Ukraine droht langfristige Ernährungsunsicherheit in Afrika''} with Tobias Heidland and Sebastian Jävervall, \textit{Megatrends Afrika - Spotlight}, April 2022. \par
    \href{https://www.welthungerhilfe.de/welternaehrung/rubriken/agrar-ernaehrungspolitik/wie-der-ukrainekrieg-afrikas-brotversorgung-trifft/}{``Ukrainekrieg bedroht langfristig Afrikas Ernährungssicherheit''} with Tobias Heidland and Sebastian Jävervall, \textit{Welternährung, Fachjournal der Welthungerhilfe}, April 2022. \par
    \href{https://www.ifw-kiel.de/publications/kiel-policy-brief/ukraine-special/long-run-impacts-of-the-conflict-in-ukraine-on-food-security-in-africa-17165/}{``Long-Run Impacts of the Conflict in Ukraine on Food Security in Africa''} with Lacina Balma, Tobias Heidland, Sebastian Jävervall, Adamon N. Mukasa, and Andinet Woldemichael, \textit{Kiel Policy Brief}, March 2022. \par
    \href{https://www.oekonomenstimme.org/artikel/2021/11/internationale-emissions--und-verteilungseffekte-eines-hoeheren-co2-preises-in-der-eu/}{``Internationale Emissions- und Verteilungseffekte eines höheren CO2-Preises in der EU''} with Thieß Petersen and Joschka Wanner, \textit{Ökonomenstimme}, November 2021. \par
\href{https://www.wirtschaftsdienst.eu/inhalt/jahr/2021/heft/11/beitrag/folgen-eines-hoeheren-co2-preises-in-der-eu-wer-gewinnt-wer-verliert.html}{``Folgen eines höheren CO2-Preises in der EU – wer gewinnt, wer verliert?''} with Thieß Petersen and Joschka Wanner, \textit{Wirtschaftsdienst}, November 2021. \par
    \href{https://www.ifw-kiel.de/publications/kiel-policy-briefs/2021/decoupling-europe-16271/}{``Decoupling Europe''} with Gabriel Felbermayr, Steffen Gans and Alexander Sandkamp, \textit{Kiel Policy Brief}, July 2021. \par
    \href{https://www.bertelsmann-stiftung.de/de/publikationen/publikation/did/eu-klimapolitik-klimaclubs-und-co2-grenzausgleich}{``EU-Klimapolitik, Klimaclubs und CO2-Grenzausgleich''} with Joschka Wanner, Gabriel Felbermayr and Sonja Peterson, Kurzstudie im Auftrag der Bertelsmann Stiftung, June 2021. \par
      \href{https://www.ifw-kiel.de/publications/policy-papers/2021/supply-chains-in-the-post-corona-era-in-german-15841/}{``Supply chains in the post-Corona era''} with Alexander Sandkamp and Gabriel Felbermayr, Expert report for the Impuls Foundation, February 2021. \par
    \href{https://www.wirtschaftsdienst.eu/inhalt/jahr/2021/heft/1/beitrag/auswirkungen-des-zweiten-shutdowns.html}{``Konjunkturschlaglicht - Auswirkungen des zweiten Shutdowns''} with Martin Ademmer and Nils Jannsen, \textit{Wirtschaftsdienst}, January 2021. \par
    \href{https://www.ifw-kiel.de/de/publikationen/policy-papers/2021/corona-krise-datenmonitor-global-0/}{``Datenmonitor global — Wie die Corona-Krise die Länder des globalen Südens trifft''}, with Julian Hinz, Katrin Kamin, Jakob Kutsch and Vincent Stamer. IfW Studie im Auftrag des Auswärtigen Amtes, December 2020. \par
\end{minipage}
\medskip

\begin{minipage}[t]{0.12\textwidth}
\hspace{0mm}
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    \href{https://www.ifw-kiel.de/publications/kiel-policy-briefs/2020/the-economic-costs-of-war-by-other-means-15301/}{``The Economic Costs of War by Other Means''}, with Sonali Chowdhry, Gabriel Felbermayr, Julian Hinz, Katrin Kamin and Anna-Katharina Jacobs. \textit{Kiel Policy Brief}, October 2020. \par
    \href{https://www.ifw-kiel.de/de/publikationen/kiel-policy-briefs/spezial/bodenbildung-in-der-binnenwirtschaft-kollaps-des-welthandels-14242/}{``Bodenbildung in der Binnenwirtschaft, Kollaps des Welthandels''}, with Gabriel Felbermayr, Julian Hinz and Vincent Stamer. \textit{Kiel Policy Brief}, May 2020. \par
    \href{https://www.ifw-kiel.de/publications/kiel-policy-briefs/special-edition/germanys-economy-in-times-of-the-corona-lockdown-14127/}{``Germany’s economy in times of the Corona Lockdown''}, with Gabriel Felbermayr and Julian Hinz. \textit{Kiel Policy Brief}, April 2020.
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CONFERENCES & SEMINARS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont CONFERENCES \& SEMINARS} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    \textit{2026} \\
    FIND Seminar, Aarhus University (\textit{planned}). \par
    \textit{2025} \\
    Paris School of Economics; ETSG in Milan; Journal of International Economics Summer School, CESifo Munich. \par
    \textit{2024} \\
    Paris School of Economics; Journal of International Economics Summer School, Oxford University; Paris-Saclay Conference on Trade and Environment; 27th Annual Conference on Global Economic Analysis, Colorado State University; ETSG, Athens; Aarhus-Kiel Trade Workshop. \par
    \textit{2023} \\
    EUI, Florence; EAERE, Cyprus; INFER \& INTECO, Valencia; ETSG, Surrey; WIFO Seminar; Junior Trade Workshop, University Mainz. \par
    \textit{2022} \\
    FIW Conference 'International Economics'; 25th Annual Conference on Global Economic Analysis, Purdue University; Kiel Institute Seminar; Environmental and Resource Economics Seminar, University of California, Berkeley.  \par
    \textit{2021} \\
    ETSG Conference, Ghent; iESF Workshop; Brown Bag Seminar, CAU Kiel; IfW Kiel. \par
    \textit{2020} \\
    Aarhus-Kiel Trade Workshop. \par
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     MEDIA APPEARANCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont SELECTED MEDIA \mbox APPEARANCE} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
  \href{https://www.dw.com/de/nach-rauswurf-wie-vertrauenswürdig-sind-us-wirtschaftsdaten-noch/audio-73561036}{``Wie vertrauenswürdig sind US-Wirtschaftsdaten noch?''}, Deutsche Welle, [\textit{podcast interview}], August 8, 2025 \par
  \href{https://www.tagesspiegel.de/internationales/verteidigung-digitales-energie-wie-wird-europa-unabhangiger-von-den-usa-14138207.html}{``Verteidigung, Digitales, Energie: Wie wird Europa unabhängiger von den USA?''}, Tagesspiegel, [\textit{own text}], August 7, 2025 \par
  \href{https://www.zeit.de/wirtschaft/2025-07/us-zoelle-handelsstreit-auswirkungen-usa}{``So hart treffen Trumps Zölle den Welthandel''}, Die Zeit, July 28, 2025 \par
  \href{https://www.srf.ch/audio/echo-der-zeit/handelszoelle-die-usa-selber-koennten-die-grosse-verliererin-sein?partId=77nj5adJX0fKQd92D0cUOK53Vmw}{``Handelszölle: Die USA selber könnten die grosse Verliererin sein''}, SRF, April 8, 2025 \par
  \href{https://on.orf.at/video/14270682/15857146/oekonom-zu-moeglichen-folgen-der-us-zoelle}{``Ökonom zu möglichen Folgen der US-Zölle''}, ORF 3 Aktuell, April 7, 2025 \par
    \href{https://www.derstandard.at/story/3000000264273/trump-stellt-china-zollnachlass-f252r-entgegenkommen-bei-tiktok-verkauf-in-aussicht}{``Wifo sieht Industrie durch US-Zölle besonders stark betroffen''}, Der Standard, April 4, 2025 \par 
    \href{https://www.derstandard.de/story/3000000256055/trumps-zoelle-koennten-usa-so-viel-kosten-wie-warren-buffett-besitzt}{``Trumps Zölle könnten USA so viel kosten wie Warren Buffetts Besitz''}, Der Standard, February 5, 2025 \par
    \href{https://www.ndr.de/nachrichten/info/Wirtschaft-Folgen-der-Staudammzerstoerung-fuer-Getreideproduktion,audio1398696.html}{``Ukraine: Folgen der Staudammzerstörung für Getreideproduktion''}, NDR Info, June 7, 2023 \par
     \href{https://www.businessinsider.de/politik/welt/spiel-auf-zeit-warum-die-bundesregierung-und-experten-glauben-dass-die-sanktionen-des-westens-russland-langfristig-in-die-knie-zwingen-werden/}{``Spiel auf Zeit: Warum die Sanktionen des Westens Russland langfristig in die Knie zwingen''}, Business Insider, July 22, 2022 \par
    ``Deal der Ukraine und Russland zu den Getreideausfuhren'', WDR 1 Cosmo, July 22, 2022 \par
    \href{https://www.zdf.de/nachrichten/heute-19-uhr/bauerntag-luebeck-oezdemir-video-100.html}{``Steigende Lebensmittelpreise nutzen den Landwirten kaum''}, ZDF heute, June 14, 2022 \par
    ``Kann Öko-Landwirtschaft die Menschen statt machen?'', WDR5, April 20, 2022 \par
    \href{https://www.wsj.com/articles/driving-into-danger-ukrainian-truckers-are-delivering-food-cargo-and-aid-11649595601}{``Driving Into Danger, Ukrainian Truckers Are Delivering Food, Cargo and Aid''} Wall Street Journal, April 10, 2022 \par
\end{minipage}
\medskip

\begin{minipage}[t]{0.12\textwidth}
\hspace{0mm}
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    ``Jetzt denkt die Regierung um - in kleinen Etappen'', Die Welt, April 5, 2022 \par
    ``Auswirkungen von EU-Sanktionen auf Russland'', arte Journal, April 5, 2022 \par
        \href{https://www.nytimes.com/2022/03/31/business/economy/diesel-economy-russia-ukraine.html}{``Soaring Cost of Diesel Ripples Through the Global Economy''} New York Times, March 30, 2022 \par
    \href{https://www.n-tv.de/wirtschaft/Wie-lange-reicht-unser-Gas-noch-article23234226.html}{``Frühwarnstufe für Gaslieferstopp: Wie lange reicht unser Gas noch?''} ntv.de, March 30, 2022 \par
    ``Krieg in der Ukraine: Gefahr für die Ernährungssicherheit in Afrika'', ARD Brennpunkt, March 21, 2022 \par
    \href{https://www.derstandard.de/story/2000134038874/krieg-heizt-die-preise-fuer-lebensmittel-weltweit-stark-an}{``Krieg heizt die Preise für Lebensmittel weltweit stark an''} Der Standard, March 12, 2022 \par
    ``Das Risiko China'', FAZ, March 11, 2022 \par
    \href{https://www.tagesspiegel.de/wirtschaft/agrarminister-cem-oezdemir-zu-den-folgen-des-kriegs-die-lebensmittelversorgung-in-deutschland-ist-sicher/28155160.html}{``Die Lebensmittelversorgung in Deutschland ist sicher''}, Der Tagesspiegel, March 11, 2022 \par
    \href{https://www.manager-magazin.de/politik/wie-es-um-die-ernaehrungssicherheit-steht-ausfall-der-ukraine-als-getreide-exporteur-trifft-afrika-hart-a-fdf304e9-e490-4d78-8cf1-f56464958af1}{``Wie der Ukraine-Krieg die weltweite Ernährung bedroht''} Manger Magazin, March 11, 2022 \par
    \href{https://www.derstandard.at/story/2000133979024/embargo-gegen-russisches-rohoel-treibt-us-preise-in-die-hoehe}{``Embargo gegen russisches Rohöl treibt US-Preise in die Höhe''}, Der Standard, March 9, 2022 \par
    Interview \href{https://www.rainews.it/tgr/tagesschau/audio/2022/03/tag-Hendrik-Mahlkow-Institut-fuer-Weltwirtschaft-Kiel-Sanktionen-Russland-Ukrainekrieg-4be0c70d-61c5-4749-9088-689b3ee625f2.html}{``Experte: 'Sanktionen führen selten zu einem Politikwechsel'''} Radio Rai, March 3, 2022 \par
    \href{https://www.sueddeutsche.de/wirtschaft/strafmassnahmen-oekonomen-spielraum-fuer-weitere-sanktionen-1.5538934}{``Ökonomen: Spielraum für weitere Sanktionen''}, Süddeutsche Zeitung, March 2, 2022 \par
    \href{https://orf.at/stories/3250156/}{``Krieg in der Ukraine: Sanktionen treffen Russland hart''} ORF, March 1, 2022 \par
    \href{https://magazin.nzz.ch/nzz-am-sonntag/international/bei-der-schaerfsten-sanktion-droht-eine-rezession-ld.1671972?reduced=true}{``Bei der schärfsten Sanktion droht eine Rezession''}, NZZ am Sonntag, February 27, 2022 \par
    \href{https://www.n-tv.de/wirtschaft/Okonom-Es-schlaegt-Viertel-vor-zwoelf-fuer-Moskau-article23155253.html}{``Ökonom: 'Es schlägt Viertel vor zwölf für Moskau'''}, ntv.de, February 25, 2022 \par
    Interview \href{https://www.hr-inforadio.de/programm/themen/ukraine-krieg-was-koennen-wirtschaftssanktionen-gegen-russland-bewirken,ukraine-konflikt-was-koennen-sanktionen-bewirken-100.html}{``Was können Wirtschaftssanktionen gegen Russland bewirken?''} hr info, February 25, 2022 \par
    \href{https://www.spiegel.de/wirtschaft/russland-und-die-eu-was-russland-wirtschaftlich-zu-verlieren-hat-a-09eb6357-9607-45f8-bfb8-d39ef5e71b86}{``Was Russland wirtschaftlich zu verlieren hat''}, Spiegel Online, February 24, 2022 \par
    Interview \href{https://www.badische-zeitung.de/die-russland-sanktionen-sind-noch-nicht-die-ganz-grosse-keule--209731804.html}{``Ökonom: 'Ein Öl- und Gas-Embargo träfe Russland erheblich'''} Badische Zeitung, February 24, 2022 \par
    \href{https://www.dw.com/de/ifw-energie-embargo-tr\%C3\%A4fe-russland-hart-deutschland-aber-kaum/a-60885585}{``IfW: Energie-Embargo träfe Russland hart - Deutschland aber kaum''} Deutsche Welle, February 23, 2022 \par
    \href{https://www.spiegel.de/wirtschaft/unternehmen/sanktionen-wegen-ukraine-eskalation-gas-boykott-wuerde-russland-am-haertesten-treffen-a-d28dc387-1c8b-498d-9470-ef15043fac74}{``Gasboykott würde Russland am härtesten treffen''} Spiegel Online, February 23, 2022 \par
    ``Das Risiko einer Rezession im Winter steigt'', FAZ, November 25, 2021 \par
    ``Willkommen im Klub'', Der Spiegel, June 26, 2021 \par
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     GRANTS & HONORS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont GRANTS AND HONORS} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    Entrepreneurship Program in Atlanta, Georgia, \emph{Joachim Herz Foundation}, 2,500 \euro{}, 2025 \par
    Add-on Fellowship, \emph{Joachim Herz Foundation}, 15,500 \euro{}, 2022 -- 2025 \par
    Research Fellowship, \emph{Fulbright Commission}, 13,000 \euro{}, 2022 \par
    Travel \& Research Fund, \emph{German Academic Exchange Service} (DAAD), 8,000 \euro{}, 2022 \par
    Wallace E. Tyner Young Researcher Award, \emph{Purdue University}, 2022 \par
    Media Award for Outstanding Outreach Activity, \emph{Kiel Institute}, 5,000 \euro{}, 2022 \par
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     MENTORED STUDENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont MENTORED STUDENTS} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    \textit{Masters} \\
    Panagiota Charalampidou (WU Vienna), Alena Pavlova (WU Vienna), Jakob Kutsch (CAU Kiel), Jakob Stender (CAU Kiel).
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     REFEREE SERVICE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont REFEREE SERVICE} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    International Economics, Review of World Economics (3x), Agricultural Economics, Empirica.
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     NON-ACADEMIC TALKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont NON-ACADEMIC TALKS} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
  \textit{2025} \\
    Talk on the impact of trade, trade policy and trade conflicts on international and German markets, North-German farmer advisory units (Agrar Beratung Nord e.V., Beratungsring NordOstsee e.V., VRS Schleswig e.V.). \par 
    \textit{2023} \\
    Talk on the effectiveness (or lack thereof) of sanctions against Russia, NATO Parliamentary Assembly --- Committee on Democracy and Security; Talk on the Impact of the War in Ukraine on Global Food Security, Forum Church and Society, \& Student Group Security Policy. \par 
    \textit{2022} \\
    Talk on the Economic Effects of the Russia Sanctions, Foreign Trade Advisory Board of the Ministry of the Economy, North Rhine-Westphalia; Talk on the Impact of the War in Ukraine on Global Food Security, Discussion Meeting with Martin Häusling and Sarah Wiener, Members of the European Parliament. \par
    \textit{2021} \\
    Talk on Climate Clubs and the EU's Carbon Border Adjustment Mechanism Proposal, Public Climate School, Cologne. \par
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont WORK EXPERIENCE} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    Research internship at Potsdam Institute for Climate Impact Research with Prof. Lotze-Campen, Research Department ``Climate Resilience'', 2017--2018
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROGRAMMING
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont PROGRAMMING} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    \textit{Proficient}: R, Git, Google Earth Engine \par
    \textit{Competent}: Python, LaTeX, GAMS, C++, JavaScript
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont LANGUAGES} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.8\textwidth}
    German (native speaker), English (bilingual proficiency)
\end{minipage}
\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.12\textwidth}
    {\fontfamily{phv}\selectfont REFERENCES} \\
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.4\textwidth}
    Prof. Gabriel Felbermayr, Ph.D. \\
    Austrian Institute of Economic Research \& \\
    Vienna University of Economics and Business \\
\href{mailto:gabriel.felbermayr@wifo.ac.at}{gabriel.felbermayr@wifo.ac.at}
\end{minipage}
\hspace{5mm}
\begin{minipage}[t]{0.4\textwidth}
    Prof. Dr. Inga Heiland \\
    Norwegian University of Science and Technology \\
\href{mailto:inga.heiland@ntnu.no}{inga.heiland@ntnu.no}
\end{minipage}
\bigskip
\bigskip

\centering{\textit{Latest updated on \today.}}

\end{document}
